### 2019-11-20 RFCs/HDF5/VOL/user_guide/body.tex
Fixed a few missing things. Did some renaming.
Former-commit-id: 29616398bccaab1347956b136990c6bc077172b4

\subsection*{The VOL Abstraction Layer}

@@

\subsection*{VOL Connectors}

@@

\subsection*{Read The Documentation For The New VOL Connector}

@@

\subsection*{Use A VOL-Enabled HDF5 Library}

@@

\subsection*{Make Sure The VOL Connector Is In The Search Path}

@@

\subsection*{Update Your Code To Load And Use A VOL Connector}

@@

\subsection*{Optional: Set The VOL Connector Via The Environment Variable}

@@

\subsection*{VOL Connector Search Path}

@@

\subsection*{registration}

@@

\subsection*{Connector Versioning}

@@

\subsection*{Connector-Specific Registration Calls}

\subsection*{\tt H5Pset\_vol()}

@@

Most connectors will provide a special API call which will make this call for you. For example, the DAOS VOL (https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol) provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call.

\subsection*{Connector Compatibility}

\subsection*{Parameter Strings}

@@

\subsection*{Environment Variable}

@@

\subsection*{Specific API Call Substitutions}
\subsection*{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}

@@

\subsection*{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_[native|data\_model]\_info()}$}

@@

\subsection*{Protect Native-Only API Calls}

@@

\section{Compatibility}
\subsection*{Introspection / Feature Flags}
\thgfuturewarning

@@

\subsection*{List of HDF5 Native VOL API Calls}

@@

\subsection*{List of HDF5 VOL-Independent API Calls}

@@

\subsection*{List of HDF5 API Calls By Callback}

>>>>

\subsection{The VOL Abstraction Layer}

@@

\subsection{VOL Connectors}

@@

\subsection{Read The Documentation For The New VOL Connector}

@@

\subsection{Use A VOL-Enabled HDF5 Library}

@@

\subsection{Make Sure The VOL Connector Is In The Search Path}

@@

\subsection{Update Your Code To Load And Use A VOL Connector}

@@

\subsection{Optional: Set The VOL Connector Via The Environment Variable}

@@

\subsection{VOL Connector Search Path}

@@

\subsection{registration}

@@

\subsection{Connector Versioning}

@@

\subsection{Connector-Specific Registration Calls}

Most connectors will provide a special API call which will set the connector in the fapl. These will often be in the form of {\tt H5Pset\_fapl\_<name>()}. For example, the DAOS VOL (https://bitbucket.hdfgroup.org/projects/HDF5VOL/repos/daos-vol) provides a {\tt H5Pset\_fapl\_daos()} API call which will take MPI parameters and make this call. See the connector's documentation or public header file(s) for more information.

\subsection{\tt H5Pset\_vol()}

@@

As mentioned above, many connectors will provide their own replacement for this call. See the connector's documentation for more information.

\subsection{Parameter Strings}

@@

\subsection{Environment Variable}

@@

\subsection{Specific API Call Substitutions}
\subsection{${\tt H5Fis\_hdf5()} \rightarrow {\tt H5Fis\_accessible()}$}

@@

\subsection{${\tt H5Oget\_info[1|2]()} \rightarrow {\tt H5Oget\_[native|data\_model]\_info()}$}

@@

\subsection{Protect Native-Only API Calls}

@@

\section{Compatibility}
\subsection{Introspection / Feature Flags}
\thgfuturewarning

@@

\subsection{List of HDF5 Native VOL API Calls}

@@

\subsection{List of HDF5 VOL-Independent API Calls}

@@

\subsection{List of HDF5 API Calls By Callback}
